R Notebook

### 2018-09-17 fitting_latemar.Rmd
rename
just the latemar here

---
title: "R Notebook"
output: html_notebook
---
we are trying here to fit all the transiogram of the co-simulation !

@@

```{r}
model<-function(h,range,b){return(exp(-abs(h/range)^2)*cos(b*h) )}
```
```{r}
c(pe1,pe2,pe3,pe4)
```

conditional proportions
```{r}

@@

```{r}
# rv1=0.3
# rv2=1.2
# rhx1=40
# rhx2=40
# b1=0
# b2=5
# rho=0.6
# shift=0.1
# rho1a<-model(shift,rv1,b1)
# warning(rho>rho1a)
# alpha1=(rho/rho1a)^2
# alpha2=1-(rho/rho1a)^2
# rv3=0.2
# rv4=0.3
# rhx3=40
# rhx4=40
# b3=0
# b4=0
# rho34=-0.6
# c=0.
# e=0.65
# a13=-0.
# a14=-0.1
# rho1a14 = model(a14,rv1,b1)

rv1=0.3
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.6
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

#thresholds
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

@@

qd1e4=qnorm(pd3e4) # no correlation with the third Gaussian function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
obje2 = Inf
obje3 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*rho1a14*rho
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e2test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
}

c(qd1e4,qd2e2,qd2e3)

@@

t33d_model=t32d_model=t23d_model=t22d_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho34
    Sigma[1,3]=Sigma[3,1]=model(d,rv3,b3)
    Sigma[1,4]=Sigma[4,1]=Sigma[2,3]=Sigma[3,2]=rho34*model(d,rv3,b3)
    Sigma[2,4]=Sigma[4,2]=(rho34^2)*model(d,rv3,b3)+(1-rho34^2)*model(d,rv4,b4)

    t22d_model[i]=pmvnorm(lower=c(qd1,qd2,qd1,qd2),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t23d_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    t32d_model[i]=pmvnorm(lower=c(-Inf,-Inf,qd1,qd2),upper=c(qd1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
    t33d_model[i]=pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(qd1,Inf,qd1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd3
}
par(mfrow=c(2,2))
t22d<-tr_2d_vert(d2,d2,30,nz,0.1)
lines(z,t22d_model)
t23d<-tr_2d_vert(d2,d3,30,nz,0.1)
lines(z,t23d_model)
t32d<-tr_2d_vert(d3,d2,30,nz,0.1)
lines(z,t32d_model)
t33d<-tr_2d_vert(d3,d3,30,nz,0.1)
lines(z,t33d_model)

td1e1_model=td1e2_model=td1e3_model=td1e4_model=td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
te1d1_model=te2d1_model=te3d1_model=te4d1_model=te1d2_model=te2d2_model=te3d2_model=te4d2_model=rep(0,300)
Sigma = diag(1,4)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=rho34
    Sigma[1,3]=Sigma[3,1]=c*model(-d-a13,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=c*(rho/rho1a)*model(a13+d-shift,rv1,b1)
    Sigma[2,3]=Sigma[3,2]=e*model(a14+d,rv1,b1)
    Sigma[2,4]=Sigma[4,2]=e*(rho/rho1a)*model(a14+d-shift,rv1,b1)
    Sigma[3,4]=Sigma[4,3]=rho

    td1e1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e2_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e3_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd1
    td1e4_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd1

    td2e1_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e3_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pd2
    td2e4_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pd2

    te1d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,-Inf),upper=c(Inf,qd2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    te2d1_model[i]=pmvnorm(lower=c(qd1,-Inf,-Inf,q2),upper=c(Inf,qd2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    te3d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,q3),upper=c(Inf,qd2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    te4d1_model[i]=pmvnorm(lower=c(qd1,-Inf,q1,-Inf),upper=c(Inf,qd2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4

    te1d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    te2d2_model[i]=pmvnorm(lower=c(qd1,qd2,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    te3d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    te4d2_model[i]=pmvnorm(lower=c(qd1,qd2,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
}

par(mfrow=c(2,4))
tr_2d_vert(d1,e1,30,nz,0.1)
lines(z,td1e1_model)
tr_2d_vert(d1,e2,30,nz,0.1)
lines(z,td1e2_model)
tr_2d_vert(d1,e3,30,nz,0.1)
lines(z,td1e3_model)
tr_2d_vert(d1,e4,30,nz,0.1)
lines(z,td1e4_model)
tr_2d_vert(d2,e1,30,nz,0.1)
lines(z,td2e1_model)
tr_2d_vert(d2,e2,30,nz,0.1)
lines(z,td2e2_model)
tr_2d_vert(d2,e3,30,nz,0.1)
lines(z,td2e3_model)
tr_2d_vert(d2,e4,30,nz,0.1)
lines(z,td2e4_model)

par(mfrow=c(4,2))
tr_2d_vert(e1,d1,30,nz,0.1)
lines(z,te1d1_model)
tr_2d_vert(e2,d1,30,nz,0.1)
lines(z,te2d1_model)
tr_2d_vert(e3,d1,30,nz,0.1)
lines(z,te3d1_model)
tr_2d_vert(e4,d1,30,nz,0.1)
lines(z,te4d1_model)
tr_2d_vert(e1,d2,30,nz,0.1)
lines(z,te1d2_model)
tr_2d_vert(e2,d2,30,nz,0.1)
lines(z,te2d2_model)
tr_2d_vert(e3,d2,30,nz,0.1)
lines(z,te3d2_model)
tr_2d_vert(e4,d2,30,nz,0.1)
lines(z,te4d2_model)

```
beautiful picture for transiograms

```{r}
png(file="latemartransiotest.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
we are showing here a figure with the transiograms on the realization
```{r}
z = (1:300)/100.
z2= (1:60)/20
png(file="latemartransiototal.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
lines(z2,t11real,lwd=0.6)
lines(z2,t11real2,lwd=0.6)
lines(z2,t11real3,lwd=0.6)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
lines(z2,t12real,lwd=0.5)
lines(z2,t12real2,lwd=0.5)
lines(z2,t12real3,lwd=0.5)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
lines(z2,t13real,lwd=0.5)
lines(z2,t13real2,lwd=0.5)
lines(z2,t13real3,lwd=0.5)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
lines(z2,t14real,lwd=0.5)
lines(z2,t14real2,lwd=0.5)
lines(z2,t14real3,lwd=0.5)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
lines(z2,t21real,lwd=0.5)
lines(z2,t21real2,lwd=0.5)
lines(z2,t21real3,lwd=0.5)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
lines(z2,t22real,lwd=0.5)
lines(z2,t22real2,lwd=0.5)
lines(z2,t22real3,lwd=0.5)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
lines(z2,t23real,lwd=0.5)
lines(z2,t23real2,lwd=0.5)
lines(z2,t23real3,lwd=0.5)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
lines(z2,t24real,lwd=0.5)
lines(z2,t24real2,lwd=0.5)
lines(z2,t24real3,lwd=0.5)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
lines(z2,t31real,lwd=0.5)
lines(z2,t31real2,lwd=0.5)
lines(z2,t31real3,lwd=0.5)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
lines(z2,t32real,lwd=0.5)
lines(z2,t32real2,lwd=0.5)
lines(z2,t32real3,lwd=0.5)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
lines(z2,t33real,lwd=0.5)
lines(z2,t33real2,lwd=0.5)
lines(z2,t33real3,lwd=0.5)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
lines(z2,t34real,lwd=0.5)
lines(z2,t34real2,lwd=0.5)
lines(z2,t34real3,lwd=0.5)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
lines(z2,t41real,lwd=0.5)
lines(z2,t41real2,lwd=0.5)
lines(z2,t41real3,lwd=0.5)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
lines(z2,t42real,lwd=0.5)
lines(z2,t42real2,lwd=0.5)
lines(z2,t42real3,lwd=0.5)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
lines(z2,t43real,lwd=0.5)
lines(z2,t43real2,lwd=0.5)
lines(z2,t43real3,lwd=0.5)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)
lines(z2,t44real,lwd=0.5)
lines(z2,t44real2,lwd=0.5)
lines(z2,t44real3,lwd=0.5)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)

lets try to fit the embedded transiograms
```{r}
rv1=0.4
rv2=1.2
rhx1=40
rhx2=40
b1=0
b2=5
rho=0.8
shift=0.1
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a)
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2
rv3=0.2
rv4=0.3
rhx3=40
rhx4=40
b3=0
b4=0
e=-0.8
f=-0.5

a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

>>>>

---
title: "R Notebook"
output: html_notebook
---
Fitting the transiograms of the Latemar

@@

Proportions of the depositional facies
```{r}
c(pe1,pe2,pe3,pe4)
```

conditional proportions of the diagenetic facies
```{r}

@@

Fitting environments of deposition
```{r}

rv1=0.3
rv2=1.2
b1=0
b2=5
rho=0.6 # correlation between Z1 and Z2
shift=0.1 # Shift between Z1 and Z2
rho1a<-model(shift,rv1,b1)
warning(rho>rho1a) # limit for the correlation between Z1 and Z2
alpha1=(rho/rho1a)^2
alpha2=1-(rho/rho1a)^2

# the thresholds are computed according to the truncation rule
# These are for the environment of deposition
q1=qnorm(pe1+pe2)
Sigma1 = matrix(c(1,rho,rho,1),2,2)
q2=0
obj = Inf
for ( test in 1:100 ){
  q2test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(-Inf,-Inf),upper=c(q1,q2test),mean=c(0,0),sigma=Sigma1) - pe1 ) 
  if (newobj < obj){
    q2 = q2test
    obj = newobj
  }
}
q3=0
obj = Inf
for ( test in 1:100 ){
  q3test = qnorm(test/100)
  newobj =abs( pmvnorm(lower=c(q1,-Inf),upper=c(Inf,q3test),mean=c(0,0),sigma=Sigma1) - pe4 ) 
  if (newobj < obj){
    q3 = q3test
    obj = newobj
  }
}

@@

@@

```
paper figure for transiograms of environment of depositions

```{r}
png(file="latemartransiotest.png",width=2000,height = 1600,res=300)
par(mar=c(2,3,1,1),mfrow=c(4,4))
t11<-tr_2d_vert(e1,e1,30,nz,0.1)
lines(z,t11_model)
title(main=expression(paste('t'[e1e1],"(h)")),line=-1)
t12<-tr_2d_vert(e1,e2,30,nz,0.1)
lines(z,t12_model)
title(main=expression(paste('t'[e1e2],"(h)")),line=-1)
t13<-tr_2d_vert(e1,e3,30,nz,0.1)
lines(z,t13_model)
title(main=expression(paste('t'[e1e3],"(h)")),line=-1)
t14<-tr_2d_vert(e1,e4,30,nz,0.1)
lines(z,t14_model)
title(main=expression(paste('t'[e1e4],"(h)")),line=-1)
t21<-tr_2d_vert(e2,e1,30,nz,0.1)
lines(z,t21_model)
title(main=expression(paste('t'[e2e1],"(h)")),line=-1)
t22<-tr_2d_vert(e2,e2,30,nz,0.1)
lines(z,t22_model)
title(main=expression(paste('t'[e2e2],"(h)")),line=-1)
t23<-tr_2d_vert(e2,e3,30,nz,0.1)
lines(z,t23_model)
title(main=expression(paste('t'[e2e3],"(h)")),line=-1)
t24<-tr_2d_vert(e2,e4,30,nz,0.1)
lines(z,t24_model)
title(main=expression(paste('t'[e2e4],"(h)")),line=-1)
t31<-tr_2d_vert(e3,e1,30,nz,0.1)
lines(z,t31_model)
title(main=expression(paste('t'[e3e1],"(h)")),line=-1)
t32<-tr_2d_vert(e3,e2,30,nz,0.1)
lines(z,t32_model)
title(main=expression(paste('t'[e3e2],"(h)")),line=-1)
t33<-tr_2d_vert(e3,e3,30,nz,0.1)
lines(z,t33_model)
title(main=expression(paste('t'[e3e3],"(h)")),line=-1)
t34<-tr_2d_vert(e3,e4,30,nz,0.1)
lines(z,t34_model)
title(main=expression(paste('t'[e3e4],"(h)")),line=-1)
t41<-tr_2d_vert(e4,e1,30,nz,0.1)
lines(z,t41_model)
title(main=expression(paste('t'[e4e1],"(h)")),line=-1)
t42<-tr_2d_vert(e4,e2,30,nz,0.1)
lines(z,t42_model)
title(main=expression(paste('t'[e4e2],"(h)")),line=-1)
t43<-tr_2d_vert(e4,e3,30,nz,0.1)
lines(z,t43_model)
title(main=expression(paste('t'[e4e3],"(h)")),line=-1)
t44<-tr_2d_vert(e4,e4,30,nz,0.1)
lines(z,t44_model)
title(main=expression(paste('t'[e4e4],"(h)")),line=-1)
```

We can find the embedded transiograms between environment of deposition
```{r}
d = 1/5.
    Sigma[1,2]=Sigma[2,1]= Sigma[3,4]=Sigma[4,3]=rho
    Sigma[1,3]=Sigma[3,1]=model(d,rv1,b1)
    Sigma[1,4]=Sigma[4,1]=(rho/rho1a)*model(abs(d+shift),rv1,b1)
    Sigma[2,3]=Sigma[3,2]=(rho/rho1a)*model(abs(d-shift),rv1,b1)
    Sigma[2,4]=Sigma[4,2]=alpha1*model(d,rv1,b1)+alpha2*model(d,rv2,b2)
    r11_model=1-pmvnorm(lower=c(-Inf,-Inf,-Inf,-Inf),upper=c(q1,q2,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r12_model=pmvnorm(lower=c(-Inf,-Inf,-Inf,q2),upper=c(q1,q2,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r13_model=pmvnorm(lower=c(-Inf,-Inf,q1,q3),upper=c(q1,q2,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe1 
    r14_model=pmvnorm(lower=c(-Inf,-Inf,q1,-Inf),upper=c(q1,q2,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe1
    r21_model=pmvnorm(lower=c(-Inf,q2,-Inf,-Inf),upper=c(q1,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r22_model=1-pmvnorm(lower=c(-Inf,q2,-Inf,q2),upper=c(q1,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r23_model=pmvnorm(lower=c(-Inf,q2,q1,q3),upper=c(q1,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r24_model=pmvnorm(lower=c(-Inf,q2,q1,-Inf),upper=c(q1,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe2
    r31_model=pmvnorm(lower=c(q1,q3,-Inf,-Inf),upper=c(Inf,Inf,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r32_model=pmvnorm(lower=c(q1,q3,-Inf,q2),upper=c(Inf,Inf,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r33_model=1-pmvnorm(lower=c(q1,q3,q1,q3),upper=c(Inf,Inf,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r34_model=pmvnorm(lower=c(q1,q3,q1,-Inf),upper=c(Inf,Inf,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe3
    r41_model=pmvnorm(lower=c(q1,-Inf,-Inf,-Inf),upper=c(Inf,q3,q1,q2),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r42_model=pmvnorm(lower=c(q1,-Inf,-Inf,q2),upper=c(Inf,q3,q1,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r43_model=pmvnorm(lower=c(q1,-Inf,q1,q3),upper=c(Inf,q3,Inf,Inf),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    r44_model=1-pmvnorm(lower=c(q1,-Inf,q1,-Inf),upper=c(Inf,q3,Inf,q3),mean=c(0,0,0,0),sigma=Sigma)/ pe4
    matrix(c(0,r12_model/r11_model,r13_model/r11_model,r14_model/r11_model,r21_model/r22_model,0,r23_model/r22_model,r24_model/r22_model,r31_model/r33_model,r32_model/r33_model,0,r34_model/r33_model,r41_model/r44_model,r42_model/r44_model,r43_model/r44_model,0),4,4,byrow=TRUE)
```

Fitting the cross-transiograms between partial dolomite and environment of depositions

```{r}
# correlations
e=-0.8 # between the first and third Gaussian random function
f=-0.5 # between the second and third Gaussian random function

# shifts 
a14=-0.1
a24=0.1
rho1a14 = model(a14,rv1,b1)
rho2a24=model(a24,rv2,b2)

# Thresholds of the third Gaussian random function
Sigmad = diag(1,3)
qd2e2=0
qd2e3=0
qd1e4=0
obje2 = Inf
obje3 = Inf
obje4 = Inf
for ( test in 1:100 ){
  qd2e2test = qnorm(test/100)
  qd2e3test = qnorm(test/100)
  qd1e4test = qnorm(test/100)
  Sigmad[1,2]=Sigmad[2,1]=e*rho1a14
  Sigmad[1,3]=Sigmad[3,1]=e*(rho/rho1a)*model(a14-shift,rv1,b1)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
  Sigmad[2,3]=Sigmad[3,2]=rho
  newobje2 =abs( pmvnorm(lower=c(qd2e2test,-Inf,q2),upper=c(Inf,q1,Inf),mean=c(0,0,0),sigma=Sigmad)/pe2 - pd2e2 ) 
  newobje3 =abs( pmvnorm(lower=c(qd2e3test,q1,q3),upper=c(Inf,Inf,Inf),mean=c(0,0,0),sigma=Sigmad)/pe3 - pd2e3 )
  newobje4 =abs( pmvnorm(lower=c(qd1e4test,q1,-Inf),upper=c(Inf,Inf,q3),mean=c(0,0,0),sigma=Sigmad)/pe4 - pd3e4 )
  if (newobje2 < obje2){
    qd2e2 = qd2e2test
    obje2 = newobje2
  }
  if (newobje3 < obje3){
    qd2e3 = qd2e3test
    obje3 = newobje3
  }
  if (newobje4 < obje4){
    qd1e4 = qd1e4test
    obje4 = newobje4
  }
}
c(qd1e4,qd2e2,qd2e3)

# cross-transiograms
td2e1_model=td2e2_model=td2e3_model=td2e4_model=rep(0,300)
td3e1_model=td3e2_model=td3e3_model=td3e4_model=rep(0,300)
Sigma = diag(1,5)
for (i in 1:300){
    d = i/100.
    Sigma[1,2]=Sigma[2,1]=Sigma[4,5]=Sigma[5,4]=rho
    Sigma[1,3]=Sigma[3,1]=e*rho1a14
    Sigma[1,4]=Sigma[4,1]=model(d,rv1,b1)
    Sigma[1,5]=Sigma[5,1]=rho*model(d+shift,rv1,b1)/rho1a
    Sigma[2,3]=Sigma[3,2]=(e*rho*model(shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(a24,rv2,b2)
    Sigma[2,4]=Sigma[4,2]=rho*model(shift-d,rv1,b1)/rho1a
    Sigma[2,5]=Sigma[5,2]=(1-(rho/rho1a)^2)*model(d,rv2,b2)+(rho^2)*model(d,rv1,b1)/(rho1a^2)
    Sigma[3,4]=Sigma[4,3]=e*model(d-a14,rv1,b1)
    Sigma[3,5]=Sigma[5,3]=(e*rho*model(d+shift-a14,rv1,b1)/rho1a)+f*sqrt(1-(rho/rho1a)^2)*model(d-a24,rv2,b2)
